### 2021-02-17 rad-icfp-2021/relwork.tex
adding some refs

\noindent \textbf{Other Language features.}
%more primitives, proved correct and more efficient. extend library

\noindent \textbf{Probabilistic Programming.}
%find something simple and precise, o.w. useless section

@@

\noindent \textbf{Limitations.}
%maybe?

\MH{useful links (Swift is close to our project, and the doc is very readable):}

\begin{verbatim}https://docs.google.com/document/d/1_BirmTqdotglwNTOcYAW-ib6mx_jl-gH9Dbg4WmHZh0/edit# \end{verbatim}
\begin{verbatim}

	https://github.com/apple/swift/blob/master/docs/DifferentiableProgramming.md#approaches-to-automatic-differentiation
\end{verbatim}

>>>>

@@

\noindent \textbf{Limitations.}
\begin{itemize}
    \item memory access for cost function 
    \item parallelism
    \item dedicated tensors for ML, and BLaS considerations
    \item implementation and benchmark
    \item conditionals
    \item recursion
    \item general HO function
    \item more 2nd order functions, though can be derived by hand once and then it's ok
    \item dynamic arrays
    \item more dynamic control flow
    \item all store vs all recompute reverse-mode, and advanced checkpointing
    \item numerical accuracy
    \item fancier types and datatypes (eg dependent, adt) 
    \item iterated ad and higher derivatives
    \item use in Probabilistic programming
    \item non smooth and partial functions, although by simply following the ref book it's as usual in AD
    \item sparsity
    \item other optimisations like implicit function theorem
\end{itemize}

\MH{useful links (Swift is close to our project, and the doc is very readable):}
\begin{verbatim}https://docs.google.com/document/d/1_BirmTqdotglwNTOcYAW-ib6mx_jl-gH9Dbg4WmHZh0/edit# \end{verbatim}
\begin{verbatim}
	https://github.com/apple/swift/blob/master/docs/DifferentiableProgramming.md#approaches-to-automatic-differentiation
\end{verbatim}
